Architectures and Open pNets

### 2018-02-11 2018-Arch-pNets/arch-pNets.tex
Minor clean-up

\todoSBin{Preliminaries on the universal(?) data domain $\data$
  and valuations.

For two valuations $\val{1}{}, \val{2}{} : V \rightarrow \data$,
we denote \[\valdiff{\val{1}{}}{\val{2}{}} \bydef{=} \setdefb{v
  \in V}{\val{1}{}(v) \neq \val{2}{}(v)}\] the set of variables
that are assigned different values by the two valuations.

To guarantee preservation of properties guards and expressions
have to be \emph{monotonic}.  In the case of a trivial order, \ie
when nothing is comparable, \emph{any guard or expression is
  monotonic}.  Thus, this is not really a constraint!
}

@@

  By \defn{comp:semantics}, a transition
%
  \begin{equation}
    \label{eq:lem1:trans:sem}
    (q_i, \val{}{i})^{i \in I} (q_j, \val{}{j})^{j \in J}
    \goesto{a, \val[\tilde]{}{}}
    (q_i', \val{\prime}{i})^{i \in I}
    (q_j', \val{\prime}{j})^{j \in J}
  \end{equation}
%  
  is a transition in $\semopen{A(\cB)}$ (\resp
  $\semopen{A'(\cB)}$) iff
%
  \begin{equation}
    \label{eq:lem1:trans}
    q_i^{i \in I} q_j^{j \in J}
    \goesto{a, G, E}
    (q_i')^{i \in I} (q_j')^{j \in J}
    \,,
  \end{equation}
%
  is a transition in $A(\cB)$ (\resp $A'(\cB)$) and
%
  \begin{mathpar}
    \val{}{i}^{i \in I} \val{}{j}^{j \in J}
    \models G
    \,,
    \and
    (\val{\prime}{i})^{i \in I} (\val{\prime}{j})^{j \in J}
    = \val[\tilde]{}{}[E]
    \,,
    \and
    \valdiff{\val{}{i}^{i \in I} \val{}{j}^{j \in J}}{
      \val[\tilde]{}{}} \subseteq \export(a)
    \,.   
  \end{mathpar}

>>>>

\noteSBin{%
  Need preliminaries on the universal(?) data domain $\data$
  and valuations.
}

\noteSBin{%
For two valuations $\val{1}{}, \val{2}{} : V \rightarrow \data$,
we denote \[\valdiff{\val{1}{}}{\val{2}{}} \bydef{=} \setdefb{v
  \in V}{\val{1}{}(v) \neq \val{2}{}(v)}\] the set of variables
that are assigned different values by the two valuations.
}

\noteSBin{%
To guarantee preservation of properties guards and expressions
have to be \emph{monotonic}.  In the case of a trivial order, \ie
when nothing is comparable, \emph{any guard or expression is
  monotonic}.  Thus, this is not really a constraint!

Do we put this in the definition of expressions and guards or in
the definitions of components and interaction models?
}

@@

  By \defn{comp:semantics}, a transition
%
  \begin{equation}
    \label{eq:lem1:trans:sem}
    (q_i, \val{}{i})^{i \in I} (q_j, \val{}{j})^{j \in J}
    \goesto{a, \val[\tilde]{}{}}
    (q_i', \val{\prime}{i})^{i \in I}
    (q_j', \val{\prime}{j})^{j \in J}
  \end{equation}
%  
  is a transition in $\semopen{A(\cB)}$ (\resp
  $\semopen{A'(\cB)}$) iff
%
  \begin{equation}
    \label{eq:lem1:trans}
    q_i^{i \in I} q_j^{j \in J}
    \goesto{a, G, E}
    (q_i')^{i \in I} (q_j')^{j \in J}
    \,,
  \end{equation}
%
  is a transition in $A(\cB)$ (\resp $A'(\cB)$) and
%
  \begin{mathpar}
    \val{i \in I}{i} \val{j \in J}{j}
    \models G
    \,,
    \and
    (\val{\prime}{i})^{i \in I} (\val{\prime}{j})^{j \in J}
    = \val[\tilde]{}{}[E]
    \,,
    \and
    \valdiff{\val{i \in I}{i} \val{j \in J}{j}}{
      \val[\tilde]{}{}} \subseteq \export(a)
    \,.   
  \end{mathpar}
